Circular Regression Trees and Forests with an Application to Probabilistic Wind Direction Forecasting

### 2020-07-06 pkg/circtree/inst/wind_paper/draft/JRSSC/rebuttal.tex

We first want to thank you for the positive feedback and your valuable input.

We agree with your comment that additional information on the calculation
requirements is valuable for the user. We have therefore listed the needed
computing time of the different methods on a standard desktop computer within
the section 'Computational details'.

\vspace{0.5em}
\begin{re}
Is it possible to include a link to computer code to reproduce your
analysis? This is not essential for publication but would be helpful for
readers who wish to perform similar analyses. The R package you have provided
for your method is very helpful in this regard.  
\end{re}

We have used data from the Austrian air navigation service provider, which
we are not at liberty to share. Hence, we are unfortunately unable to provide
code and data to reproduce the application. However, as you have already
pointed out, the implementation of circular regression trees and forests is
provided in a freely available R package with examples included in the documentation.
Independent of this publication, we are planning to provide an updated online
platform for the whole `partykit' project in the near future.

@@

First of all we want to thank you for your positive feedback and valuable input.

Indeed, information criteria like AIC or BIC are natural candidates for
determining the model order in distributional models, i.e., the number of splits
in distributional trees. While they could be used instead of the $p$-values in
the ``internal stopping'' or ``pre-pruning'', they are typically considered
for ``post-pruning'' after initially growing a large tree (e.g., in
Su~\emph{et al.}~2004 or Zeileis~\emph{et al.}~2008). This is now discussed
in Appendix~A along with the other details of the tree algorithm employed.
There we also refer to the recent work of Schlosser~\emph{et al.}~2019
which empirically investigates the performance of different pre- and post-pruning
strategies in unbiased recursive partitioning. This work finds that post-pruning
only improves the performance of the unbiased trees considered when the
underlying tests do not work well, e.g., when the power of the tests is low
or the sample size extremely large.

\vspace{0.5em}
\begin{re}
I would like to point out related works on circular regression models for
shape representation (Kashyap and Chellappa) and circular random forests for
vehicle direction estimation (Hara and Chellappa) given below. I feel there is
some overlap between this paper and the work of Hara and Chellappa on using
circular statistics for vehicle orientation estimation. The authors may include
some comparisons with Hara, Chellappa work.
\end{re}

Thank you very much for pointing out these interesting references that, unfortunately,
we were not aware of before. We now briefly discuss the work of Hara and Chellappa~(2017),
comparing their approach to ours in Sect.~1.1. The main difference is that their
algorithm aims at conditional mean estimation for circular data and only adopts
distributional aspects for determining the number of splits. Specifically, the
variances are restricted to be shared across splits whereas in the method proposed they
are full model parameters that are estimated and tested along with the means.

### 2020-07-06 pkg/circtree/inst/wind_paper/draft/draft.Rnw
Include minor adaptions by Reto and Lisa
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@3052 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 6eed4d3a3cc88dd5c226902b9644142d414c116b

The computation time on a standard computer is in the order of milliseconds for
the circular fit (used for the persistency and the climatological model),
seconds for the estimation of the linear model and the circular tree, and from
a few minutes up to an hour for the estimation of the circular forest; the
latter strongly depends on the number of covariates employed and, hence, varies
between the two locations included in the application. However, for a single
station and forecast step, the persistency model must be re-estimated for each
time of interest, independent climatological and linear models have to be
fitted for all times of interest within a single calendar year, whereas for all
times of interest only a single circular tree and a single circular forest
model is required. In general with respect to other applications, the computation
time for the estimation of circular regression trees and forests can be reduced by
various implemented settings, such as, e.g., the use of additional CPU cores or
binning of the input data (c.f.  Section~\ref{sec:wind:models}).

@@

Subsequently, the same testing and splitting procedure is repeated in each of
the resulting subgroups until some stopping criterion is reached. Complementing
the pre-pruning mentioned above, based on the significance level of the
statistical tests, further criteria such as maximal tree depth or a minimal
number of observations in a node can be employed.

>>>>

The computation time on a standard computer is in the order of milliseconds for
the circular fit (used for the persistency and the climatological model),
seconds for the estimation of the linear model and the circular tree, and from
a few minutes up to an hour for the estimation of the circular forest; the
latter strongly depends on the number of covariates employed and, hence, varies
between the two locations included in the application. However, for a single
station and forecast step, the persistency model must be re-estimated for each
time of interest, independent climatological and linear models have to be
fitted for all times of interest within a single calendar year, whereas for all
times of interest only a single circular tree and a single circular forest
model is required. In general with respect to other applications, the computation
time for the estimation of circular regression trees and forests can be reduced by
various implemented settings, such as, e.g., parallel estimation on multiple
CPU cores or binning of the input data (c.f.  Section~\ref{sec:wind:models}).

@@

Subsequently, the same testing and splitting procedure is repeated in each of
the resulting subgroups until some stopping criterion is reached. Complementing
the pre-pruning based on the significance level of the
statistical tests, as mentioned above, further criteria such as maximal tree depth or a minimal
number of observations in a node can be employed.
